% resume.tex
%
% (c) 2002 Matthew M. Boedicker <mboedick@mboedick.org> http://mboedick.org
% $Id: resume.tex,v 1.7 2004/02/02 14:21:06 mboedick Exp $
%
\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage[pdftitle={Patrick T. Ramsey},colorlinks=true,urlcolor=blue]{hyperref}
\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\textbf{Patrick T. Ramsey}  & \\
3620 17th St.  & (508) 333-6120 \\
Apt. B & ptr@ptr.xyz \\
San Francisco, CA 94114 & \\
\end{tabular*}
\\
\vspace{0.1in}
{\large \textbf{Education}}

	\begin{itemize}
	\item 
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Brown University} & Providence, RI \\
		Computer Science A.B., December 2007 & \\
	\end{tabular*}

	\end{itemize}

{\large \textbf{Technical Skills}}

\begin{itemize}
    \item Python (scikit-learn, Twisted, Django), Javascript (AngularJS), Java (Android, Cordova), Kotlin, HTML/CSS, C, Postgresql
    \item Managed applications in AWS using EC2, CloudFront, RDS, S3, Redshift, Lambda, CloudFormation
\end{itemize}

{\large \textbf{Work History}}

\begin{itemize}
    \item
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
            \textbf{Software Engineer} & September 2013 --- Present \\
            \href{http://www.fivestars.com/}{Fivestars Loyalty, Inc.} & San Francisco, CA \\
        \end{tabular*}
        \begin{itemize}
            \item Developed a service using machine learning to identify and extract transaction data from receipts in printer output.  Currently handles roughly 500,000 documents per day from $>$ 1200 merchants.
            \item Designed and built a reverse proxy and virtual receipt printer as a native plugin to our cordova-android loyalty app.
            \item Collaborated to design and build an Android-based direct API integration between our loyalty product and Clover's point of sale.
            \item Singlehandedly migrated our production Postgres instance from Heroku to Amazon RDS with an hour of downtime and no issues.
            \item Helped to develop a harness using CEF to port our Javascript/Cordova-based client from Android to Windows XP+, replacing our
                old Qt-based native app.  Wrote the auto-updater that allowed pushing out the new application to replace the old one.
            \item Mentored three interns, who each made meaningful and lasting contributions to the aforementioned receipt data extraction service and Windows client.
            \item In two months, and with two other engineers, developed the tooling that deployed our production services for four years.
            \item Helped build AutoPilot, a feature that allows triggered notifications and offers based on user behavior, which allowed us to triple what we charged to the majority of our merchants
            \item Wrote service to monitor office bathrooms for availability.
        \end{itemize}
    \item
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
            \textbf{Software Engineer} & January 2011 --- September 2013 \\
            \href{http://www.cloudera.com/}{Cloudera, Inc.} & Palo Alto, CA \\
        \end{tabular*}
        \begin{itemize}
            \item Maintained rpm/debian packaging for Cloudera build toolchain and earned committership on the \href{http://bigtop.apache.org/}{Apache Bigtop} project.
            \item Developed, enhanced and maintained engineering infrastructure in a highly heterogeneous large scale environment.  Scaled configuration management and OS provisioning to 850 hosts.
        \end{itemize}
    \item
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
            \textbf{Junior Linux Systems Administrator} & December 2009 --- December 2010 \\
            \href{http://www.limewire.com/}{Lime Company} & New York, NY \\
        \end{tabular*}
        \begin{itemize}
            \item Assisted in infrastructure planning, coding, and deployment of a new music store application to AWS.
            \item Assisted in administration and maintenence of production infrastructure
        \end{itemize}

    \item
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
            \textbf{Software Engineer} & January 2008 --- December 2009 \\
            \href{http://www.amie.st/}{Amie Street, Inc.} & Long Island City, NY \\
        \end{tabular*}
        \begin{itemize}
            \item Developed a large and extensible content ingestion and backup system in python, and managed the ingestion component of our integration with a major music label
        \end{itemize}
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{itemize}

\end{document}
